SIR Model With Testing Flows and Isolation

### 2020-12-15 codes/ali_test_sir.Rmd
seperate code and plottings

# DFE; analytic approach
# Su <- Su_dfe(params)
# Sn <- Sn_dfe(params)
# state_dfe <- c(S_u=Su, S_n=Sn,
#                 I_u=0,I_n=0,I_p=0,I_t=0,
#                 R_u=0,R_n=0,R_p=0,R_t=0,
#                 N=0,P=0)
# check:
all.equal(c(state_dfe[["S_u"]],state_dfe[["S_n"]]),roots_dfe$root)
```

@@

```{r plot_run1, warning=FALSE}
gg1 <- (ggplot(data=out2, aes(x=time,y=value,col=compartment))
    + geom_line()
    + scale_y_log10(limits=c(0.1,params[["N0"]]))
##    + scale_x_continuous(limits=c(0,240))
)
direct.label(gg1,"last.bumpup")
```

@@

```{r plot_long, warning=FALSE}
direct.label(gg1 %+% out_long2,"last.bumpup")
```

@@

### Contour plot of $R_0=1$ and interpretations approache 1
```{r contour_R0_1, message=FALSE,warning=FALSE }
n_out <- 5 ## facets (rows/cols)
n_in <- 41 ## grid N within facets
 # specify the ranges
 beta  <- 0.339  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=n_out)
 eta_c <- seq(0,1, length.out=n_out) #0.001 to 0.5 
 rho     <- seq(0,0.01, length.out=n_in)
 omega <- seq(0.1,2 , length.out=n_in) #note omega must be > rho, was 0.011
 W_S <- 0.3 #choose 0.3 for TTI testing plan and 1 for the random testing.

 df1 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=params[["gamma"]],omega=omega,rho=rho,
                    W_S=W_S,W_I=params[["W_I"]],W_R=params[["W_R"]],
                    p_S=params[["p_S"]],p_I=params[["p_I"]],p_R=params[["p_R"]],
                    eta_w=eta_w,eta_c=eta_c,s=params[["s"]])

# Need to be corrected: in F_I, state_dfe should be changed according to the df1!
df2<- data.frame(df1,R0=apply(df1,1,function(params_in)R0(params=params_in)),
                      Fi= apply(df1,1,function(params_in)F_I(params=params_in)))

df2 <- df2 %>% dplyr::mutate(R0_sub = ifelse(eta_w<eta_c, NA, R0))  
```

```{r}
## hacked (not very robustly) to chain label_both() and label_parsed() ...
label_special <- function (labels, multi_line=FALSE, sep = "== ") {
    value <- ggplot2:::label_value(labels, multi_line = multi_line)
    variable <- ggplot2:::label_variable(labels, multi_line = multi_line)
    variable[[1]] <- gsub("_(.)$","[\\1]",variable[[1]])
    ## not using multiple faceting variables on each margin, so forget paste
    out <- Map(paste, variable, value, sep = sep)
    out[[1]] <- lapply(out[[1]], function(expr) c(parse(text=expr)))
    out
}
```

```{r show_contours_1, width=24,height=24,message=FALSE,warning=FALSE}
brks_vec <- seq(0.8,1.05,by=0.05) # Break vector for unifying the legends in Random and TTI testing cases.

p1 <- ggplot(df2,aes(x=omega,y=rho,z=R0_sub))+ theme_bw() +
  xlab(TeX('$\\omega$, Returning test result rate (1/day)')) +
  ylab(TeX('$\\rho$, testing intensity (1/day per capita)')) +
  theme(panel.spacing=grid::unit(0,"lines"),legend.position = c(0.89, 0.73)) # initial theme, comment it for TTI testing plot
  # theme(panel.spacing=grid::unit(0,"lines"),legend.position = "none") #AG, uncomment for Random Case
p1_temp <- (p1
    + geom_contour_filled(breaks=brks_vec)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    # + scale_fill_manual(palette=mycolors(brks_vec),drop=FALSE)
    + facet_grid(eta_w~eta_c, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"),drop=FALSE)
    + ggtitle(TeX(sprintf("W_S=%.1f, W_I=W_R=1",W_S)))
    + geom_rect(data=df2, fill=ifelse(df2$eta_c>df2$eta_w,"grey90","NA" ),
                          color= NA,
                          ymin=-1,
                          ymax=10,
                          xmin=-1,
                          xmax=2)
    )
p1_temp

## BMB: FIXME: probably wrong but ... ???
## ggsave(p1_temp,filename = "R0contour_random.pdf" , path="../pix/")

### Contour plot of $R_0=1$ and interpretations approache 2, parametrization $s=\eta_w/\eta_c$

```{r contour_R0_2, message=FALSE,warning=FALSE }
# This part is done to carry our simulation when s=eta_c/eta_w is involved. Also to fill the upper triangle panels in the panel plot. 
#  # specify the ranges
# beta  <- 0.339  ## set beta high enough to allow R0>1 in worst case 
# rho     <- seq(0,0.01, length.out=n_in)
# omega <- seq(0.1,2 , length.out=n_in) #note omega must be > rho, 
# eta_c <- seq(0.001,0.1, length.out=n_out)
# s <- seq(1,10,length.out=n_out) 
# 
#  df11 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=params[["gamma"]],omega=omega,rho=rho,
#                     W_S=W_S,W_I=params[["W_I"]],W_R=params[["W_R"]],
#                     p_S=params[["p_S"]],p_I=params[["p_I"]],p_R=params[["p_R"]],
#                     eta_w=params[["eta_w"]],eta_c=eta_c,s=s)
# 
# df22<- data.frame(df11,R0=apply(df11,1,function(params_in)R02(params=params_in)),
#                       Fi= apply(df11,1,function(params_in)F_I(params=params_in)),
#                        Sn=apply(df11,1,function(params_in)Sn_dfe(params = params_in)))

```{r show_contours_2, width=24,height=24,message=FALSE,warning=FALSE}
# p11 <- ggplot(df22,aes(x=omega,y=rho,z=R0))+ theme_bw() +
#     theme(panel.spacing=grid::unit(0,"lines"))
# p2_temp <- (p11
#     + geom_contour_filled(breaks=pretty(unique(df22$R0),5),
#                           alpha=0.5) ## breaks=0.2)
#     + geom_contour(breaks=1,alpha=0.5,colour="black")
#     + facet_grid(s~eta_c, labeller=label_special)
#     + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_fill_viridis_d(name=parse(text="R[0]"),breaks=brks_vec)
#     + ggtitle("W[S]=1, W[I]=W[R]=1")
# )
# p2_temp
# ## ggsave(p2_temp,filename = "R0contour_random_s.png" , path="../pix/")
# # ggsave(p2_temp,filename = "R0contour_random_s.pdf" , path="../pix/")
```

@@

```{r  chnages of R0 wrt omega,message=FALSE,warning=FALSE }

>>>>

# check if the DFE is the same in numerical and analytic:
all.equal(c(state_dfe[["S_u"]],state_dfe[["S_n"]]),roots_dfe$root)
```

@@

```{r plot_run1, warning=FALSE}
gg1 <- (ggplot(data=out2, aes(x=time,y=value,col=compartment))
            + theme_bw()
            + geom_line()
            + ylab(label="Prevalence")
            + xlab(label="Time (days)")
            + scale_y_log10(limits=c(0.1,params[["N0"]]))
            + xlim(0,310)
)
direct.label(gg1,"last.bumpup")
```

@@

```{r plot_long, warning=FALSE}
p_temp <- direct.label(gg1 %+% out_long2,"last.bumpup")
p_temp
ggsave(p_temp,filename = "sir_sing.pdf" ,
       width = 14, height = 14, units = "cm",
       path="../pix/")
```

@@

### Contour plot of $R_0=1$ and interpretations approache 1
 <!-- Run sir.plot.R -->

@@
